Logarithmic Space Verifiers on NP-complete

### 2019-11-14 doc/manuscript.tex
Updated the content proof

Nevertheless, the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ cannot be equal to the family of languages $\textit{1TAPE}[T'(n)]$ for some function $G(n) > 1$. Certainly, for a sufficiently large instance of size $n$, then we can consume all the amount of possible configurations during the computation in a deterministic one-way Turing machines with $T'(\frac{n}{G(n)})$ work tape, whereas we could still compute more configurations in a deterministic one-way Turing machines with $T'(n)$ work tape for the same instance because of $T'(\frac{n}{G(n)}) < T'(n)$. Indeed, there are languages in $\textit{1TAPE}[T'(n)]$ that cannot be decided in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ due to the lack of computational space for the acceptance or rejection of the instances. Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}. In general, we can assume the same result for every small amount of work tape $T(n)$ when $T(n)$ is a monotonically increasing function.
\end{proof}

>>>>

Nevertheless, the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ cannot be equal to the family of languages $\textit{1TAPE}[T'(n)]$ for some function $G(n) > 1$. Certainly, for a sufficiently large instance of size $n$, then we can consume all the amount of possible configurations during the computation in a deterministic one-way Turing machines with $T'(\frac{n}{G(n)})$ work tape, whereas we could still compute more configurations in a deterministic one-way Turing machines with $T'(n)$ work tape for the same instance. Indeed, there are languages in $\textit{1TAPE}[T'(n)]$ that cannot be decided in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ due to the lack of computational space for the acceptance or rejection of the instances. Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}. In general, we can assume the same result for every small amount of work tape $T(n)$ when $T(n)$ is a monotonically increasing function.
\end{proof}
